--Decide between "The structure of tensor categories via local topological field theory" (Noah and CSP prefer) and "Tensor categories and local topological field theory" (CD prefers).

--Do we want a table of contents?

--Finish the introduction once CSP has had a look at it.

--Add CSP's thanks (Jamie and Bruce?)

--Fight about left and right.

--Make sure "twisted bimodule" language is propagated throughout the paper.

--Add some more info about how to translate between bimodule categories and categories of bimodules, in the service of showing that ENO's Radford proof agrees with ours.

--Make sure global dimension statements deal with fusion/multi-fusion issues.

--Add a quick reference for notations at the end of section 2 (e.g. finite = blah, linear = blah, etc.)

--Switch the order of 2.6 and 2.7, move some material accordingly.  Add some key facts about fusion categories (automatically exact over Vec, hence functors out are exact and have explicit form, separability in characteristic 0).

--Remove Radford stuff from background, and add to new Section 6.4.

--Rewrite exposition in the beginning of Section 3.2.

--CD double-check Section 3.3.

--Write intro paragraph.

--Add Radford example to Section 4.1.

--Example 4.1

--Go through section 5 and fix assumptions.

--Someone other than me should read my proof of Thm 5.1 and possibly clean it up.

--Put the (m,n)-category notation somewhere in section 3.

--Section 5.3 should give the definition which follows from the original proofs in the first column, and then have the balanced description in the next column.

--Section 5.4 needs to be redone in light of separability.

--Lots of stuff in Section 6.

--check, dual, L, R notation propagation.

--Rearrange anomaly conjectures into 7.4 and change ENO conjectures to questions.

--Add discussion of Z(C) to section 7.